---
title: "Self-esteem across the menstrual cycle"
date: '2023'
output: github_document
---

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library("plotrix")
```

```{r, include = FALSE}
# specifying the path name
path <- "dados.xlsx"
  
# importing the required library
library(rio)
  
# reading data from all sheets
data <- import_list(path)
  
```

```{r}
brutos = data$`Dados_brutos (3)`
head(brutos)
```

#parse target
```{r}

for (i in 1:nrow(brutos)){
  if(substr(brutos$TARGET[i],nchar(brutos$TARGET[i])-2,nchar(brutos$TARGET[i])) == "til"){
    brutos$TARGET[i] = "inútil"  
  }
}


```

#check 
```{r}
brutos %>%
  mutate(new = case_when(TARGET == "alegre" ~ "positive",
                         TARGET =="capaz" ~ "positive",
                         TARGET == "confiante" ~ "positive",
                         TARGET == "genial" ~ "positive",
                         TARGET == "linda" ~ "positive"
                                ,TRUE ~ 'negative'
                                )) %>% pull(new) -> new

a = new == brutos$PRIME_VAL 
soma = sum(a, na.rm = TRUE) # best way to count TRUE values
soma == length(a)
```

#check participant's id
```{r}

summary(factor(brutos$participant))

#to lower case all cols
names(brutos) <- tolower(names(brutos))

brutos$participant = tolower(brutos$participant)

#brutos %>% group_by(participant) %>% count()
```
#### Apa theme
```{r}
#apa
theme_apa <- function(base_size = 12, base_family = "", box = FALSE) {
  adapted_theme <- ggplot2::theme_bw(base_size, base_family) +
    ggplot2::theme(
      plot.title = ggplot2::element_text(size = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(14), 0), hjust = 0.5)
      , plot.subtitle = ggplot2::element_text(size = ggplot2::rel(0.8), margin = ggplot2::margin(ggplot2::rel(-7), 0, ggplot2::rel(14), 0), hjust = 0.5)

      # , axis.title = ggplot2::element_text(size = ggplot2::rel(1.1))
      , axis.title.x = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(ggplot2::rel(12), 0, 0, 0))
      , axis.title.x.top = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(12), 0))
      , axis.title.y = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, ggplot2::rel(12), 0, 0))
      , axis.title.y.right = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(12)))
      , axis.ticks.length = ggplot2::unit(ggplot2::rel(6), "points")
      , axis.text = ggplot2::element_text(size = ggplot2::rel(0.9))
      , axis.text.x = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(ggplot2::rel(6), 0, 0, 0))
      , axis.text.y = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, ggplot2::rel(6), 0, 0))
      , axis.text.y.right = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(6)))
      , axis.line = ggplot2::element_line()
      # , axis.line.x = ggplot2::element_line()
      # , axis.line.y = ggplot2::element_line()

      , legend.title = ggplot2::element_text()
      , legend.key = ggplot2::element_rect(fill = NA, color = NA)
      , legend.key.width = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.key.height = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.margin = ggplot2::margin(
        t = ggplot2::rel(16)
        , r = ggplot2::rel(16)
        , b = ggplot2::rel(16)
        , l = ggplot2::rel(16)
        , unit = "points"
      )

      , panel.spacing = ggplot2::unit(ggplot2::rel(14), "points")
      , panel.grid.major.x = ggplot2::element_blank()
      , panel.grid.minor.x = ggplot2::element_blank()
      , panel.grid.major.y = ggplot2::element_blank()
      , panel.grid.minor.y = ggplot2::element_blank()

      , strip.background = ggplot2::element_rect(fill = NA, color = NA)
      , strip.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, ggplot2::rel(10), 0))
      , strip.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(10)))
    )

  if(box) {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_rect(color = "black"))
  } else {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_blank())
  }

  adapted_theme
}

```

```{r}
plot = ggplot(data = brutos, aes(x = prime_type, y = rt, fill = interaction(correct,prime_type))) + geom_boxplot() + facet_wrap(~phase) + theme_apa()

plot
```

```{r}
brutos2 = brutos %>% group_by(phase, prime_type, prime_val,target) %>% summarize(soma = sum(correct)) 

for (i in 1:nrow(brutos2)){
  if(brutos2$prime_type[i] == "OTHER"){
    brutos2$soma[i] = brutos2$soma[i]/5
  }
}

brutos2

brutos2%>% 
  ggplot(aes(x = target, y = soma, fill = prime_val)) +
    geom_bar(position="dodge",stat = "identity")+
    #scale_fill_manual(values = c ('royalblue1', 'grey2', 'yellow1'))+
    ylab("Values")+
    xlab("")+
    facet_grid(prime_type ~ phase) + theme_apa()+
  theme(axis.text.x = element_text(angle = 95, vjust = 0.5,hjust = 1)) -> plot

plot
```
#filter by beautiful and ugly
```{r}
brutos2 %>% subset(target %in% c("linda","feia")) %>% 
  ggplot(aes(x = target, y = soma, fill = prime_val)) +
    geom_bar(position="dodge",stat = "identity")+
    #scale_fill_manual(values = c ('royalblue1', 'grey2', 'yellow1'))+
    ylab("Values")+
    xlab("")+
    facet_grid(prime_type ~ phase) + theme_apa()+
  theme(axis.text.x = element_text(angle = 95, vjust = 0.5,hjust = 1)) 
```
```{r}
#brutos = brutos %>% subset(target %in% c("linda","feia")) 
```

```{r}
brutos %>% group_by(participant, phase) %>% summarize(soma = sum(correct)) %>% arrange(desc(soma)) ->grafico
```

```{r}
ggplot(grafico, aes(x = reorder(participant, -soma), y = soma)) + geom_bar(position="dodge",stat = "identity") +  coord_flip()+ facet_wrap(~phase) #+ geom_hline(yintercept=, linetype="dashed", 
      #          color = "red", size=2)

```

```{r}
#brutos %>% group_by(participant, phase) %>% tally() %>% arrange(n)
```


```{r}
#brutos %>% group_by(participant, phase) %>% summarise_at(vars(rt), funs(rt_mean = mean(., na.rm = T))) %>% arrange(desc(rt_mean))
```

#remove participants mj690 & cc522
*few responses
*few corrects
*high rt
```{r}
brutos = brutos %>% subset(!(participant %in% c("mj690","cc522","sm247")))
```

#missing responses-add to dataframe
```{r}
codes = c("ma889","ma929","mr971","na210","nj267","va606")

p1=list("ma889",0,1,0.42,0,1,"negative","SELF","x","x","menstruation")
p2=list("ma929",0,4,0.42,0,2,"negative","SELF","x","x","menstruation")
p3=list("mr971",0,4,0.42,0,2,"negative","SELF","x","x","ovulation")
p4=list("na210",0,2,0.42,0,2,"positive","SELF","x","x","menstruation")
p5=list("nj267",0,3,0.42,0,1,"negative","SELF","x","x","menstruation")
p6=list("va606",0,1,0.42,0,1,"positive","SELF","x","x","menstruation")

nested = list(p1,p2,p3,p4,p5,p6)
df_nested <-  as.data.frame(do.call(rbind, nested))

colnames(df_nested) = colnames(brutos)

library(tidyr)
unnested = df_nested %>% unnest(colnames(df_nested))
unnested = data.frame(unnested)
colnames(unnested) = colnames(brutos)

brutos = rbind(brutos,unnested)

```

# POSITIVITY INDEX - SELF
```{r}
brutos %>% group_by(participant,phase,bloco, prime_val, prime_type) %>% summarize(soma = sum(correct)) -> df

taxa = c()
x = 25
y = 5
  
for (i in 1:nrow(df)){
  if(df$prime_type[i] == "OTHER"){
    taxa = c(taxa,(df$soma[i]/x))
  } 
  else{
    taxa = c(taxa,(df$soma[i]/y))
  }
}

df$taxa = taxa
```
#don't
```{r, eval = FALSE}
data= data.frame(matrix(ncol=7,nrow = 0))
colnames(data) = colnames(df)

blocks = c(1,2,3,4,5)

#for each participant
for (participant in levels(factor(df$participant))){
  #for each phase
  for(phase in phases){
    #for each block
    for (block in blocks){
      
            data[nrow(data) + 1,] =list(participant,phase,block, "negative","OTHER",0,0)
            
            data[nrow(data) + 1,] =list(participant,phase,block, "negative","SELF",0,0)

            data[nrow(data) + 1,] =list(participant,phase,block, "positive","OTHER",0,0)
            data[nrow(data) + 1,] =list(participant,phase,block, "positive","SELF",0,0)
    
    }
  }
}
```

#don't
```{r, eval = FALSE}
df = rbind(df,data)
df%>% group_by(participant,phase,bloco, prime_val, prime_type) %>% summarize(taxa = sum(taxa))->df

```

```{r}
index = c()
bloco = 1
counter = 1

for(i in 1:(nrow(df)-2)){
  if (df$bloco[i+2] == bloco & counter < 3){
    index = c(index,df$taxa[i]-df$taxa[i+2])
  }
  else {
    bloco = df$bloco[i+2]
  }
  if (counter == 4){
    counter = 0
  }
  counter = counter+1
}

```


#create dataframe
```{r}
participants = levels(factor(df$participant))
participants = rep(participants, each = 20)


phase = rep(c("menstruation","ovulation"), each = 10, times = 10)

bloco = rep(c(1,2,3,4,5),each = 2,times = 100)

condition = rep(c("OTHER","SELF"),times = 500)

colunas = c("participant","phase","bloco","condition","index")

df_index = data.frame(participants,phase,bloco,condition, index) 
colnames(df_index) = colunas

```

#remove participants
```{r}
df %>% subset(!(participant %in% c("sp123","sm247","mj690","cc522"))) -> df
```


```{r}
df_index %>% group_by(phase,condition) %>% summarise_at(vars(index), funs(rt_mean = mean(., na.rm = T))) 
```
#symmetric index
```{r}
df_index$index = -df_index$index
```

```{r}
ggplot(data = df_index, aes(x = condition, y = index, color = phase)) + geom_boxplot() + theme_apa()
```

```{r}
#head(df,20)
```

```{r}
#df_index %>% group_by(participant,phase,condition) %>% summarise_at(vars(index), funs(rt_mean = mean(., na.rm = T))) %>% arrange(rt_mean)

```


#remove outlier
```{r}
df_index = df_index %>% subset(participant!="ij887" & participant != "mr971") 
```


```{r}
hist(df_index$index)
```

```{r}
df_index %>% group_by(phase,condition) %>% summarise_at(vars(index), funs(index = mean(., na.rm = T)))-> df_index2 
df_index %>% group_by(phase,condition) %>% summarise_at(vars(index), funs(se = std.error(., na.rm = T))) %>% pull(se) ->se

df_index2$se = se

# Create bar plot with error bars
ggplot(df_index2, aes(x = condition, y = index, fill = phase)) +
  geom_bar(stat = "identity",position = position_dodge(0.9)) +   scale_fill_manual(values = c("brown2", "Tan1")) +
  geom_errorbar(aes(ymin = index - se, ymax = index + se), width = 0.2,position = position_dodge(0.9)) + theme_apa()


```


```{r}
df_index %>% group_by(participant,phase,condition) %>% summarise_at(vars(index), funs(index = mean(., na.rm = T))) %>% ggplot(aes(x = condition, y = index, color = phase)) + geom_boxplot() +theme_apa()
```

```{r}
library(lme4)
library(afex)
df_index$participant = factor(df_index$participant)
df_index$phase = factor(df_index$phase)
df_index$bloco = factor(df_index$bloco)
df_index$condition = factor(df_index$condition)

model = lmer(index~condition*phase + (1|participant), df_index)

summary(model)

```


```{r}
library(emmeans)
noise <- emmeans(model,~condition*phase)


x = contrast(noise, "pairwise", simple = "each", combine = TRUE, adjust="bonf")
x
```

### ESCALAS ###
```{r, include = FALSE}
# specifying the path name
path <- "escalas.xlsx"

# importing the required library
library(rio)
  
# reading data from all sheets
data <- import_list(path)
  
```

```{r}
rosenberg = data$Rosenberg
hp = data$HP
```

```{r}
rosenberg %>% select(CODE,M_Ros_F1,M_Ros_F2) ->rosenberg
hp %>% select(CODE, M_HP_P_1,M_HP_P_2,M_HP_S_1,M_HP_S_2,M_HP_A_1,M_HP_A_2)->hp
```

```{r}
head(hp)
```

```{r}
library(reshape2)
# Melt the data frame to long format using two conditions
hp = hp %>%
  pivot_longer(cols = starts_with("M_HP_"), 
               names_to = c("condition", "phase"), 
               names_pattern = c("(M_HP_[PSA]_)([12])")) 

colnames(hp)[1] = "participant"

hp$participant = tolower(hp$participant)

hp <- hp %>%
  mutate(phase = if_else(phase == "1", "ovulation", "menstruation"))

```

#rename participants' codes
```{r}
hp %>%
  mutate(participant = case_when(participant == "av116"~"ab116",
                         participant == "mj960"~"bj960",
                         participant ==  "sp513"~"sj513",
                         participant ==  "mj714"~"mm714",
                         participant == "ms416"~"sm416" ,
                         participant == "af8411"~ "af841",
                         participant == "fb968" ~"mb968",
                         participant == "rj073" ~"rj673",
                        TRUE ~ participant
                                ))-> hp


```

#left join
```{r}
length(levels(df_index$participant))


df_merged <- df_index %>%
  left_join(hp, by = c("participant","phase"))

df_merged %>%
  mutate(condition.y = case_when(condition.y == "M_HP_P_"~"Performance",
                         condition.y == "M_HP_S_"~"Social",
                         condition.y ==  "M_HP_A_"~"Attractiveness"
                                ))-> df_merged

df_merged$participant = factor(df_merged$participant)

head(df_merged)
```

```{r}
ggplot(data = df_merged, aes(x = condition.y, y = value, color = phase)) + geom_boxplot() + theme_apa()
```

```{r}
df_merged %>% group_by(phase,condition.y) %>% summarise_at(vars(value), funs(value = mean(., na.rm = T)))-> df_merged2 

df_merged %>% group_by(phase,condition.y) %>% summarise_at(vars(value), funs(se = std.error(., na.rm = T))) %>% pull(se) ->se

df_merged2$se = se

# Create bar plot with error bars
ggplot(df_merged2, aes(x = condition.y, y = value, fill = phase)) +
  geom_bar(stat = "identity",position = position_dodge(0.9)) +   scale_fill_manual(values = c("brown2", "Tan1")) +
  geom_errorbar(aes(ymin = value - se, ymax = value + se), width = 0.2,position = position_dodge(0.9)) + theme_apa()


```





#using hp scale as predictor of index
#wide format
```{r}
df_wide <- df_merged %>%
  pivot_wider(id_cols = c(participant, phase, bloco, condition.x, index),
              names_from = condition.y,
              values_from = value)
head(df_wide)
```
#subtract index of self-other
```{r}
index = c()
for (i in 1:nrow(df_wide)-1){
  if(i%%2!=0){
  index = c(index,df_wide$index[i+1]-df_wide$index[i])
  }
}  
length(index)*2

#create dataframe
participants = levels(factor(df_wide$participant))
participants = rep(participants, each = 10)


phase = rep(c("menstruation","ovulation"), each = 10, times = 24)

bloco = rep(c(1,2,3,4,5),each = 2,times = 48)

#condition = rep(c("OTHER","SELF"),times = 500)

colunas = c("participant","phase","bloco","index_global")

df_index = data.frame(participants,phase,bloco, index) 
colnames(df_index) = colunas


df_wide %>% group_by(participant,phase,bloco) %>% summarize(Attractiveness = mean(Attractiveness)) %>% pull(Attractiveness) -> Attractiveness

df_wide %>% group_by(participant,phase,bloco) %>% summarize(Social = mean(Social)) %>% pull(Social) -> Social

df_wide %>% group_by(participant,phase,bloco) %>% summarize(Performance = mean(Performance)) %>% pull(Performance) -> Performance

df_index$Performance = Performance
df_index$Attractiveness = Attractiveness
df_index$Social = Social

head(df_index)
```

```{r}
df_index$bloco = factor(df_index$bloco)


model = lmer(Attractiveness~phase + (1|participant), df_index)
summary(model)
```

```{r}

model = lmer(Social~phase + (1|participant), df_index)
summary(model)
```

```{r}

model = lmer(Performance~phase + (1|participant), df_index)
summary(model)
```

```{r}
ggplot(data = df_index, aes(x = phase, y = index_global)) + geom_boxplot() + theme_apa()
```
```{r}
df_index %>% group_by(phase) %>% summarise_at(vars(index_global), funs(value = mean(., na.rm = T)))-> df_index2 

df_index %>% group_by(phase) %>% summarise_at(vars(index_global), funs(se = std.error(., na.rm = T))) %>% pull(se) ->se

df_index2$se = se

# Create bar plot with error bars
ggplot(df_index2, aes(x = phase, y = value, fill = phase)) +
  geom_bar(stat = "identity",position = position_dodge(0.9)) +   scale_fill_manual(values = c("brown2", "Tan1")) +
  geom_errorbar(aes(ymin = value - se, ymax = value + se), width = 0.2,position = position_dodge(0.9)) + theme_apa()


```


```{r}

model = lmer(index_global~phase + (1|participant), df_index)

summary(model)


```

#Predicting global index using Attractiveness/phase
```{r}

model = lmer(index_global~Attractiveness*phase + (1|participant), df_index)

summary(model)


```


```{r}
library("interactions")
interact_plot(model, pred = Attractiveness, modx = phase) + theme_apa()
```


```{r}
head(rosenberg)
```

```{r}
# Melt the data frame to long format using two conditions
rosenberg %>%
  pivot_longer(cols = starts_with("M_"), 
               names_to = c("condition", "phase"), 
               names_pattern = c("(M_HP_[PSA]_)([12])")) -> rosenberg2


rosenberg2$participant = tolower(rosenberg2$CODE)

phase = rep(c("menstruation","ovulation"), each = 1, times = 53)

rosenberg2$phase = phase
rosenberg2$rosenberg = rosenberg2$value

rosenberg = rosenberg2 %>% select (participant,phase,rosenberg)
```


#rename participants' codes
```{r}
rosenberg %>%
  mutate(participant = case_when(participant == "av116"~"ab116",
                         participant == "mj960"~"bj960",
                         participant ==  "sp513"~"sj513",
                         participant ==  "mj714"~"mm714",
                         participant == "ms416"~"sm416" ,
                         participant == "af8411"~ "af841",
                         participant == "fb968" ~"mb968",
                         participant == "rj073" ~"rj673",
                        TRUE ~ participant
                                ))-> rosenberg


```

```{r}
df_merged3 <- df_index %>%
  left_join(rosenberg, by = c("participant","phase"))
```

```{r}
ggplot(data = df_merged3, aes(x = phase, y = rosenberg)) + geom_boxplot() + theme_apa()

```

```{r}
#standardize

model = lmer(rosenberg ~ phase + (1|participant), df_merged3)
summary(model)


```