---
title: "Self-esteem across the menstrual cycle"
date: '2023'
output: github_document
---

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library("plotrix")
library(sjPlot)
```

```{r, include = FALSE}
# specifying the path name
path <- "dados.xlsx"
  
# importing the required library
library(rio)
  
# reading data from all sheets
data <- import_list(path)
  
```

```{r}
brutos = data$`Dados_brutos (3)`
head(brutos)
```

#parse target
```{r}

for (i in 1:nrow(brutos)){
  if(substr(brutos$TARGET[i],nchar(brutos$TARGET[i])-2,nchar(brutos$TARGET[i])) == "til"){
    brutos$TARGET[i] = "inútil"  
  }
}


```

#check  
```{r}
brutos %>%
  mutate(new = case_when(TARGET == "alegre" ~ "positive",
                         TARGET =="capaz" ~ "positive",
                         TARGET == "confiante" ~ "positive",
                         TARGET == "genial" ~ "positive",
                         TARGET == "linda" ~ "positive"
                                ,TRUE ~ 'negative'
                                )) %>% pull(new) -> new

a = new == brutos$PRIME_VAL 
soma = sum(a, na.rm = TRUE) # best way to count TRUE values
soma == length(a)
```

#check participant's id
```{r}

summary(factor(brutos$participant))

#to lower case all cols
names(brutos) <- tolower(names(brutos))

brutos$participant = tolower(brutos$participant)

#brutos %>% group_by(participant) %>% count()
```
```{r}
library(extrafont)
#font_import("C:/Users/nunok/AppData/Local/Microsoft/Windows/Fonts")

loadfonts()
#available_fonts <- windowsFonts()
#print(available_fonts)
```

#### Apa theme
```{r}
#apa
theme_apa <- function(base_size = 12, base_family = "NewsGotT", box = FALSE) {
  adapted_theme <- ggplot2::theme_bw(base_size, base_family) +
    ggplot2::theme(
      plot.title = ggplot2::element_text(size = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(14), 0), hjust = 0.5)
      , plot.subtitle = ggplot2::element_text(size = ggplot2::rel(0.8), margin = ggplot2::margin(ggplot2::rel(-7), 0, ggplot2::rel(14), 0), hjust = 0.5)

      # , axis.title = ggplot2::element_text(size = ggplot2::rel(1.1))
      , axis.title.x = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(ggplot2::rel(12), 0, 0, 0))
      , axis.title.x.top = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(12), 0))
      , axis.title.y = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, ggplot2::rel(12), 0, 0))
      , axis.title.y.right = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(12)))
      , axis.ticks.length = ggplot2::unit(ggplot2::rel(6), "points")
      , axis.text = ggplot2::element_text(size = ggplot2::rel(0.9))
      , axis.text.x = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(ggplot2::rel(6), 0, 0, 0))
      , axis.text.y = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, ggplot2::rel(6), 0, 0))
      , axis.text.y.right = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(6)))
      , axis.line = ggplot2::element_line()
      # , axis.line.x = ggplot2::element_line()
      # , axis.line.y = ggplot2::element_line()

      , legend.title = ggplot2::element_text()
      , legend.key = ggplot2::element_rect(fill = NA, color = NA)
      , legend.key.width = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.key.height = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.margin = ggplot2::margin(
        t = ggplot2::rel(16)
        , r = ggplot2::rel(16)
        , b = ggplot2::rel(16)
        , l = ggplot2::rel(16)
        , unit = "points"
      )

      , panel.spacing = ggplot2::unit(ggplot2::rel(14), "points")
      , panel.grid.major.x = ggplot2::element_blank()
      , panel.grid.minor.x = ggplot2::element_blank()
      , panel.grid.major.y = ggplot2::element_blank()
      , panel.grid.minor.y = ggplot2::element_blank()

      , strip.background = ggplot2::element_rect(fill = NA, color = NA)
      , strip.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, ggplot2::rel(10), 0))
      , strip.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(10)))
    )

  if(box) {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_rect(color = "black"))
  } else {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_blank())
  }

  adapted_theme
}

```

```{r}
plot = ggplot(data = brutos, aes(x = prime_type, y = rt, fill = interaction(correct,prime_type))) + geom_boxplot() + facet_wrap(~phase) + theme_apa()

plot
```

```{r}
brutos2 = brutos %>% group_by(phase, prime_type, prime_val,target) %>% summarise(soma = sum(correct)) 

for (i in 1:nrow(brutos2)){
  if(brutos2$prime_type[i] == "OTHER"){
    brutos2$soma[i] = brutos2$soma[i]/5
  }
}

brutos2

brutos2%>% 
  ggplot(aes(x = target, y = soma, fill = prime_val)) +
    geom_bar(position="dodge",stat = "identity")+
    #scale_fill_manual(values = c ('royalblue1', 'grey2', 'yellow1'))+
    ylab("Values")+
    xlab("")+
    facet_grid(prime_type ~ phase) + theme_apa()+
  theme(axis.text.x = element_text(angle = 95, vjust = 0.5,hjust = 1)) -> plot

plot
```
#filter by beautiful and ugly
```{r}
brutos2 %>% subset(target %in% c("linda","feia")) %>% 
  ggplot(aes(x = target, y = soma, fill = prime_val)) +
    geom_bar(position="dodge",stat = "identity")+
    #scale_fill_manual(values = c ('royalblue1', 'grey2', 'yellow1'))+
    ylab("Values")+
    xlab("")+
    facet_grid(prime_type ~ phase) + theme_apa()+
  theme(axis.text.x = element_text(angle = 95, vjust = 0.5,hjust = 1)) 
```

```{r}
brutos2 %>%  group_by(phase,prime_type, prime_val) %>% summarise(soma = mean(soma)) %>% 
  ggplot(aes(x = prime_val, y = soma)) +
    geom_bar(position="dodge",stat = "identity")+
    #scale_fill_manual(values = c ('royalblue1', 'grey2', 'yellow1'))+
    ylab("Values")+
    xlab("")+
    facet_grid(prime_type ~ phase) + theme_apa()+
  theme(axis.text.x = element_text(angle = 95, vjust = 0.5,hjust = 1)) 
```

```{r}
#brutos = brutos %>% subset(target %in% c("linda","feia")) 
```

```{r}
brutos %>% group_by(participant, phase) %>% summarise(soma = sum(correct)) %>% arrange(desc(soma)) ->grafico
```
```{r}
brutos %>% filter(participant == "sm247" & phase == "ovulation")
```

```{r}
ggplot(grafico, aes(x = reorder(participant, -soma), y = soma)) + geom_bar(position="dodge",stat = "identity") +  coord_flip()+ facet_wrap(~phase) #+ geom_hline(yintercept=, linetype="dashed", 
      #          color = "red", size=2)

```

```{r}
IQR(grafico$soma)

ovulation = subset(grafico, phase == "ovulation")
IQR(ovulation$soma)

ovulation

ovulation = subset(ovulation, participant!="sm247")

boxplot(ovulation$soma)

```
```{r}
menstruation = subset(grafico, phase == "menstruation")
IQR(menstruation$soma)
menstruation$soma
```
```{r}

menstruation = subset(grafico, phase  == "menstruation")
tail(menstruation$soma)
tail(menstruation$participant,2)
boxplot(menstruation$soma)


```

```{r}
#brutos %>% group_by(participant, phase) %>% tally() %>% arrange(n)
```


```{r}
#brutos %>% group_by(participant, phase) %>% summarise_at(vars(rt), funs(rt_mean = mean(., na.rm = T))) %>% arrange(desc(rt_mean))
```

#remove participants mj690 & cc522 
*few responses
*few corrects
*high rt
```{r}
brutos = brutos %>% subset(!(participant %in% c("mj690","cc522","sm247")))

```

#ROC-CURVE
```{r}
head(brutos)

response = c()
for (i in 1:nrow(brutos)){
  if (brutos$prime_val[i] == "positive"){
    if (brutos$correct[i] == 1){
      response = c(response, 1)
    }
    else{
      response = c(response,0)
    }
  }
  else{
    if(brutos$correct[i] == 1){
      response = c(response,0)
    }
    else{
      response = c(response,1)
    }
    
  }
}

expected = response

library(caTools)

library(pROC)

response = c()
for (i in 1:nrow(brutos)){
  if(brutos$prime_val[i]=="positive"){
    response = c(response,1)
  }
  else{
    response = c(response,0)
  }
}



test_roc = roc(expected ~ response, plot = TRUE, print.auc = TRUE)

roc_df = data.frame(brutos$phase,brutos$prime_type,expected,response)


self_ovulation_df = roc_df %>% subset(brutos.phase == "ovulation" & brutos.prime_type=="SELF")
self_menstruation_df = roc_df %>% subset(brutos.phase == "menstruation" & brutos.prime_type=="SELF")

other_ovulation_df = roc_df %>% subset(brutos.phase == "ovulation" & brutos.prime_type=="OTHER")
other_menstruation_df = roc_df %>% subset(brutos.phase == "menstruation" & brutos.prime_type=="OTHER")



# create ROC curves for each condition
roc1 <- roc(self_ovulation_df$expected,self_ovulation_df$response)
roc2 <- roc(self_menstruation_df$expected,self_menstruation_df$response)

roc3 = roc(other_ovulation_df$expected,other_ovulation_df$response)
roc4 = roc(other_menstruation_df$expected,other_menstruation_df$response)

ggroc(list(self_ovulation = roc1, self_menstruation = roc2, other_ovulation = roc3, other_menstruation = roc4 )) +
   scale_color_manual(values = c("self_ovulation"="brown2","self_menstruation" = "Tan","other_ovulation" = "blue","other_menstruation" ="green"),
                      labels = c(paste0("self ovulation ",'ROC Curve ', '(AUC = ', .74, ')')
                                 ,paste0("self menstruation ",'ROC Curve ', '(AUC = ',.71, ')')
                                 ,paste0("other ovulation ",'ROC Curve ', '(AUC = ', .73, ')')
                                 ,paste0("other menstruation ",'ROC Curve ', '(AUC = ', .73, ')'))) + theme_apa()




```


#missing responses-add to dataframe
```{r}
codes = c("ma889","ma929","mr971","na210","nj267","va606")

p1=list("ma889",0,1,0.42,0,1,"negative","SELF","x","x","menstruation")
p2=list("ma929",0,4,0.42,0,2,"negative","SELF","x","x","menstruation")
p3=list("mr971",0,4,0.42,0,2,"negative","SELF","x","x","ovulation")
p4=list("na210",0,2,0.42,0,2,"positive","SELF","x","x","menstruation")
p5=list("nj267",0,3,0.42,0,1,"negative","SELF","x","x","menstruation")
p6=list("va606",0,1,0.42,0,1,"positive","SELF","x","x","menstruation")

nested = list(p1,p2,p3,p4,p5,p6)
df_nested <-  as.data.frame(do.call(rbind, nested))

colnames(df_nested) = colnames(brutos)

library(tidyr)
unnested = df_nested %>% unnest(colnames(df_nested))
unnested = data.frame(unnested)
colnames(unnested) = colnames(brutos)

brutos = rbind(brutos,unnested)

```

# POSITIVITY INDEX - SELF
```{r}
brutos %>% group_by(participant,phase,bloco, prime_val, prime_type) %>% summarise(soma = sum(correct)) -> df

taxa = c()
x = 25
y = 5
  
for (i in 1:nrow(df)){
  if(df$prime_type[i] == "OTHER"){
    taxa = c(taxa,(df$soma[i]/x))
  } 
  else{
    taxa = c(taxa,(df$soma[i]/y))
  }
}

df$taxa = taxa
```


```{r}

index = c()
bloco = 1
counter = 1

for(i in 1:(nrow(df)-2)){
  if (df$bloco[i+2] == bloco & counter < 3){
    index = c(index,df$taxa[i]-df$taxa[i+2])
  }
  else {
    bloco = df$bloco[i+2]
  }
  if (counter == 4){
    counter = 0
  }
  counter = counter+1
}

```


#create dataframe
```{r}
participants = levels(factor(df$participant))
participants = rep(participants, each = 20)


phase = rep(c("menstruation","ovulation"), each = 10, times = 10)

bloco = rep(c(1,2,3,4,5),each = 2,times = 100)

condition = rep(c("OTHER","SELF"),times = 500)

colunas = c("participant","phase","bloco","condition","index")

df_index = data.frame(participants,phase,bloco,condition, index) 
colnames(df_index) = colunas

```


#remove spanish participant
```{r}
df_index %>% subset(!(participant %in% c("sp123"))) -> df_index
```


```{r}
df_index %>% group_by(phase,condition) %>% summarise_at(vars(index), funs(rt_mean = mean(., na.rm = T))) 
```
#symmetric index
```{r}
df_index$index = -df_index$index
```

```{r}
ggplot(data = df_index, aes(x = condition, y = index, color = phase)) + geom_boxplot() + theme_apa()
```
```{r}
df_index %>% group_by(participant,condition, phase) %>% summarise_at(vars(index), funs(rt_mean = mean(., na.rm = T))) %>% arrange(rt_mean) 
```

```{r}
#head(df,20)
```

```{r}
#df_index %>% group_by(participant,phase,condition) %>% summarise_at(vars(index), funs(rt_mean = mean(., na.rm = T))) %>% arrange(rt_mean)

```


#remove outlier
```{r}
#df_index = df_index %>% subset(participant!= "sp123" & participant!="sm247" & participant!= "mj690" & participant!="cc522")

#df_index = df_index %>% subset(participant!="ij887" & participant != "mr971")  
#df_index = df_index %>% subset(participant != "mr971")  
```


```{r}
hist(df_index$index)
```

```{r}
df_index

```

```{r}
df_index %>% group_by(phase,condition) %>% summarise_at(vars(index), funs(index = mean(., na.rm = T)))-> df_index2 
df_index %>% group_by(phase,condition) %>% summarise_at(vars(index), funs(se = std.error(., na.rm = T))) %>% pull(se) ->se

df_index2$se = se

my_color <- rgb(213,211, 213, maxColorValue = 255)
my_color2 <- rgb(255,254, 255, maxColorValue = 255)

# Create bar plot with error bars
ggplot(df_index2, aes(x = condition, y = index, fill = phase)) +
  geom_bar(stat = "identity",position = position_dodge(0.9),color = "black") +   scale_fill_manual(values = c(my_color, my_color2),labels=c('Menstruation', 'Ovulation')) +
  geom_errorbar(aes(ymin = index - se, ymax = index + se), width = 0.2,position = position_dodge(0.9)) + theme_apa() + xlab("Prime Type") + ylab("Positivity Index") +
scale_x_discrete(labels = c("Self","Other")) + labs(fill = "Phase of the Menstrual Cycle") 

```


```{r}
df_index %>% group_by(participant,phase,condition) %>% summarise_at(vars(index), funs(index = mean(., na.rm = T))) %>% ggplot(aes(x = condition, y = index, color = phase)) + geom_boxplot() +theme_apa()
```

```{r}
library(lme4)
library(afex)
df_index$participant = factor(df_index$participant)
df_index$phase = factor(df_index$phase)
df_index$bloco = factor(df_index$bloco)
df_index$condition = factor(df_index$condition)
```


### check contrabalanceamento
```{r}
contrabalanceamento = read.csv("contrabalanceamento.csv")
```

```{r}
#to lower case all cols
names(contrabalanceamento) <- tolower(names(contrabalanceamento))

contrabalanceamento$participant = tolower(contrabalanceamento$participant)
```

#left-join
```{r}
df_index = df_index %>% left_join(contrabalanceamento)
```

```{r}
#model = lmer(index~condition*phase + tecla + contrabalanceamento+fase_start +(1|participant), df_index) 

#tab_model(model)
```


# REPORT MAIN MODEL IMPLICIT
```{r}
model = lmer(index~condition*phase +(1|participant), df_index)

tab_model(model)

```

```{r}
summary(model)
```
```{r}

library(report)
report(model)
```

```{r}
library(emmeans)
#noise <- emmeans(model,~condition*phase)


#x = contrast(noise, "pairwise", simple = "each", combine = TRUE, adjust="bonf")
#x
```


### ESCALAS ###
```{r, include = FALSE}
# specifying the path name
path <- "escalas.xlsx"

# importing the required library
library(rio)
  
# reading data from all sheets
data <- import_list(path)
  
```

```{r}
rosenberg = data$Rosenberg

#rosenberg %>% subset(!(CODE %in% c("sp123"))) -> rosenberg
hp = data$HP
```



```{r}
rosenberg %>% dplyr::select(CODE,M_Ros_F1,M_Ros_F2) ->rosenberg
hp %>% dplyr::select(CODE, M_HP_P_1,M_HP_P_2,M_HP_S_1,M_HP_S_2,M_HP_A_1,M_HP_A_2)->hp
```


```{r}
head(hp)
```

```{r}
library(reshape2)
# Melt the data frame to long format using two conditions
hp = hp %>%
  pivot_longer(cols = starts_with("M_HP_"), 
               names_to = c("condition", "phase"), 
               names_pattern = c("(M_HP_[PSA]_)([12])")) 

colnames(hp)[1] = "participant"

hp$participant = tolower(hp$participant)

hp <- hp %>%
  mutate(phase = if_else(phase == "1", "ovulation", "menstruation"))

```

#rename participants' codes
```{r}
hp %>%
  mutate(participant = case_when(participant == "av116"~"ab116",
                         participant == "mj960"~"bj960",
                         participant ==  "sp513"~"sj513",
                         participant ==  "mj714"~"mm714",
                         participant == "ms416"~"sm416" ,
                         participant == "af8411"~ "af841",
                         participant == "fb968" ~"mb968",
                         participant == "rj073" ~"rj673",
                        TRUE ~ participant
                                ))-> hp


```

#right join
```{r}
length(levels(factor(df_index$participant)))


df_merged <- df_index %>%
  right_join(hp, by = c("participant","phase"))

df_merged %>%
  mutate(condition.y = case_when(condition.y == "M_HP_P_"~"Performance",
                         condition.y == "M_HP_S_"~"Social",
                         condition.y ==  "M_HP_A_"~"Attractiveness"
                                ))-> df_merged

df_merged$participant = factor(df_merged$participant)

#remove sp123 -- spanish
df_merged = subset(df_merged, participant!="sp123")

```

```{r}
ggplot(data = df_merged, aes(x = condition.y, y = value, color = phase)) + geom_boxplot() + theme_apa()
```

```{r}
df_merged %>% group_by(phase,condition.y) %>% summarise_at(vars(value), funs(value = mean(., na.rm = T)))-> df_merged2 

df_merged %>% group_by(phase,condition.y) %>% summarise_at(vars(value), funs(se = std.error(., na.rm = T))) %>% pull(se) ->se

df_merged2$se = se

# Create the color using RGB values
my_color <- rgb(213,211, 213, maxColorValue = 255)
my_color2 <- rgb(255,254, 255, maxColorValue = 255)

# Create bar plot with error bars
ggplot(df_merged2, aes(x = condition.y, y = value, fill = phase)) +
  geom_bar(stat = "identity",position = position_dodge(0.9), color = "black") +   scale_fill_manual(values = c(my_color, my_color2), labels=c('Menstruation', 'Ovulation')) +
  geom_errorbar(aes(ymin = value - se, ymax = value + se), width = 0.2,position = position_dodge(0.9)) + theme_apa() + xlab("Self-esteem Domain") + ylab("Mean Scores") + scale_x_discrete(labels = c("Physical", "Performance", "Social")) + labs(fill = "Phase of the Menstrual Cycle") 


```

#using hp scale as predictor of index
#wide format
```{r}
#df_merged[,c("participant","phase","bloco","condition.x","index","condition.y","bloco")]

df_wide <- df_merged[,c("participant","phase","bloco","condition.x","index","condition.y","value")] %>%
  pivot_wider(id_cols = c(participant, phase, bloco, condition.x, index),
              names_from = condition.y,
              values_from = value)

df_wide
```
#subtract index of self-other
```{r}

index = c()
for (i in 1:nrow(df_wide)-1){
  
  if(i%%2!=0){
  index = c(index,df_wide$index[i+1]-df_wide$index[i])
  }
}  

length(index)*2

#create dataframe
#participants = levels(factor(df_wide$participant))
participants = unique(df_wide$participant)
participants = rep(participants, each = 10)


phase = rep(c("menstruation","ovulation"), each = 5, times = 52)

bloco = rep(c(1,2,3,4,5),each = ,times = 104)

#condition = rep(c("OTHER","SELF"),times = 500)

colunas = c("participant","phase","bloco","index_global")

#adjust nas
zeros = rep(0,521-494)
index = c(index,zeros) 
index[491] = 0
index[492] = 0
index[493] = 0
length(index)
  
df_index = data.frame(participants,phase,bloco, index) 
colnames(df_index) = colunas


df_wide %>% group_by(participant,phase,bloco) %>% summarise(Attractiveness = mean(Attractiveness)) %>% pull(Attractiveness) -> Attractiveness

df_wide %>% group_by(participant,phase,bloco) %>% summarise(Social = mean(Social)) %>% pull(Social) -> Social

df_wide %>% group_by(participant,phase,bloco) %>% summarise(Performance = mean(Performance)) %>% pull(Performance) -> Performance

#df_index$Performance = Performance
#df_index$Attractiveness = Attractiveness
#df_index$Social = Social

```

```{r}
df_wide = df_wide %>% left_join(contrabalanceamento)
```
```{r}
ggplot(aes(x = phase, y = Attractiveness, colour = phase), data = df_wide) + geom_boxplot()
```
```{r}
df_wide %>% group_by(participant, phase) %>% summarise(Attractiveness) %>% arrange(Attractiveness)
```
#reduced_scales
```{r}
df_wide$bloco = factor(df_wide$bloco)

reduced_scales = df_wide %>% group_by(participant,phase, Performance, Social, Attractiveness, contrabalanceamento, fase_start) %>% summarise(Performance = mean(Performance), Attractiveness = mean(Attractiveness), Social = mean(Social))

#model = lmer(Attractiveness~phase+contrabalanceamento+fase_start+(1|participant), reduced_scales)
model = lmer(Attractiveness~phase+(1|participant), reduced_scales)

tab_model(model)
```
```{r}
summary(model)
```

```{r}
#plot_model(model, type = "pred", terms = c("contrabalanceamento","phase"))
```

```{r}
#plot_model(model, type = "pred", terms = c("contrabalanceamento","fase_start","phase"))
```


```{r}
library(emmeans)
noise <- emmeans(model,~phase)


x = contrast(noise, "pairwise", simple = "each", combine = TRUE, adjust="bonf")
x
```

```{r}
eff_size(noise, sigma=sigma(model), edf = df.residual(model))
```

```{r}

#model = lmer(Social~phase + contrabalanceamento+ fase_start+(1|participant), reduced_scales)

model = lmer(Social~phase + (1|participant), reduced_scales)
tab_model(model)
```

```{r}
summary(model)
```

```{r}
#plot_model(model, type = "pred", terms = c("contrabalanceamento","phase"))
```

```{r}
#plot_model(model, type = "pred", terms = c("contrabalanceamento","phase"))
```

```{r}
noise <- emmeans(model,~phase)


x = contrast(noise, "pairwise", simple = "each", combine = TRUE, adjust="bonf")
x
```

```{r}
eff_size(noise, sigma=sigma(model), edf = df.residual(model))
```

```{r}
#model = lmer(Performance~phase+contrabalanceamento + fase_start + (1|participant), reduced_scales)
model = lmer(Performance~phase + (1|participant), reduced_scales)
tab_model(model)
```

```{r}
summary(model)
```

```{r}
#plot_model(model, type = "pred", terms = c("contrabalanceamento","phase"))
```
```{r}
#plot_model(model, type = "pred", terms = c("contrabalanceamento","fase_start","phase"))
```

```{r}
noise <- emmeans(model,~phase)


x = contrast(noise, "pairwise", simple = "each", combine = TRUE, adjust="bonf")
x
```

```{r}
eff_size(noise, sigma=sigma(model), edf = df.residual(model))
```

#número de participantes por condição
```{r}
#df_index %>% group_by(phase,fase_start,contrabalanceamento) %>% summarise(numero = n()/5)
```

```{r}
ggplot(data = df_index, aes(x = phase, y = index_global)) + geom_boxplot() + theme_apa()
```


```{r}
df_index %>% group_by(phase) %>% summarise_at(vars(index_global), funs(value = mean(., na.rm = T)))-> df_index2 


df_index %>% group_by(phase) %>% summarise_at(vars(index_global), funs(se = std.error(., na.rm = T))) %>% pull(se) ->se

df_index2$se = se



# Load required packages
library(ggplot2)
library(viridis)
library(ggthemes)


# Create the color using RGB values
my_color <- rgb(213,211, 213, maxColorValue = 255)
my_color2 <- rgb(255,254, 255, maxColorValue = 255)

# Create bar plot with error bars and thinner outlines
ggplot(df_index2, aes(x = phase, y = value, fill = phase)) +
  geom_bar(stat = "identity", position = position_dodge(0.9), color = "black", size = 0.5) +
  scale_fill_manual(values = c(my_color, my_color2), labels=c('Menstruation', 'Ovulation')) +
  geom_errorbar(aes(ymin = value - se, ymax = value + se), width = 0.2, position = position_dodge(0.9)) +
  theme_apa() + scale_x_discrete(labels = c("Self","Other")) + labs(fill = "Phase of the Menstrual Cycle") + xlab("Prime Type Condition") + ylab("Global Positivity Index") + ylim(-0.01,0.1)


ggplot(df_index, aes(x = phase, y = index_global)) + geom_boxplot() + theme_apa() 


```


```{r}

model = lmer(index_global~phase+(1|participant), df_index)

tab_model(model)

```

```{r}
summary(model)
```

```{r}
noise <- emmeans(model,~phase)


x = contrast(noise, "pairwise", simple = "each", combine = TRUE, adjust="bonf")
x
```

```{r}
eff_size(noise, sigma=sigma(model), edf = df.residual(model))
```


```{r}
#df_index
#model = lmer(index_global~Attractiveness*phase + Social*phase + Performance*phase + (1|participant), df_index)

#tab_model(model)


#df_index
```


```{r}
#library("interactions")
#interact_plot(model, pred = Attractiveness, modx = phase) + theme_apa()
```


```{r}
head(rosenberg)
```

```{r}
# Melt the data frame to long format using two conditions
rosenberg %>%
  pivot_longer(cols = starts_with("M_"), 
               names_to = c("condition", "phase"), 
               names_pattern = c("(M_HP_[PSA]_)([12])")) -> rosenberg2


rosenberg2$participant = tolower(rosenberg2$CODE)

phase = rep(c("menstruation","ovulation"), each = 1, times = 53)

rosenberg2$phase = phase
rosenberg2$rosenberg = rosenberg2$value

rosenberg = rosenberg2 %>% select (participant,phase,rosenberg)
```

```{r}
#rosenberg %>% subset(!(participant %in% c("sp123"))) -> rosenberg
model = lmer(rosenberg~phase + (1|participant), data = rosenberg)
tab_model(model)
```

```{r}
summary(model)
```

```{r}
"sp123" %in% levels(factor(rosenberg$participant))
```

#rename participants' codes
```{r}
rosenberg %>%
  mutate(participant = case_when(participant == "av116"~"ab116",
                         participant == "mj960"~"bj960",
                         participant ==  "sp513"~"sj513",
                         participant ==  "mj714"~"mm714",
                         participant == "ms416"~"sm416" ,
                         participant == "af8411"~ "af841",
                         participant == "fb968" ~"mb968",
                         participant == "rj073" ~"rj673",
                        TRUE ~ participant
                                ))-> rosenberg


```

```{r}
df_merged3 <- df_wide %>%
  right_join(rosenberg, by = c("participant","phase"))
```

```{r}
ggplot(aes(x = phase, y = rosenberg), data = df_merged3) + geom_boxplot() + theme_apa()
```

#remove spanish "sp123"
```{r}
rosenberg = subset(rosenberg, participant!="sp123")
```

```{r}
rosenberg %>% group_by(phase) %>% summarise_at(vars(rosenberg), funs(value = mean(., na.rm = T)))-> df_index2 

rosenberg %>% group_by(phase) %>% summarise_at(vars(rosenberg), funs(se = std.error(., na.rm = T))) %>% pull(se) ->se

df_index2$se = se

# Create bar plot with error bars
ggplot(df_index2, aes(x = phase, y = value, fill = phase)) +
  geom_bar(stat = "identity",position = position_dodge(0.2), width = 0.5) +   scale_fill_manual(values = c("brown2", "Tan1")) +
  geom_errorbar(aes(ymin = value - se, ymax = value + se), width = 0.2,position = position_dodge(0.9)) + theme_apa()

#ggplot(df_index, aes(x = phase, y = index_global)) + geom_boxplot() + theme_apa()

```
```{r}
reduced = df_merged3 %>% group_by(participant,phase) %>% summarise(rosenberg = mean(rosenberg))

reduced = subset(reduced, participant!="sp123")

model = lmer(rosenberg ~ phase +(1|participant), reduced)
tab_model(model)

#model = lmer(rosenberg ~ phase + contrabalanceamento + fase_start + (1|participant), reduced)
#tab_model(model)
```

```{r}
summary(model)
```

#Check correlations
```{r}
df_merged3 = subset(df_merged3, participant!="sp123")
df_merged3 %>% group_by(participant,phase) %>% summarise_at(c("index", "Performance","Social","Attractiveness", "rosenberg"), mean, na.rm = TRUE) -> df_corr

# Remove columns with NA values
df_corr <- na.omit(df_corr)

df_corr$Performance = scale(df_corr$Performance)

df_corr$Social = scale(df_corr$Social)

df_corr$Attractiveness = scale(df_corr$Attractiveness)

df_corr$index = scale(df_corr$index)

correlation_matrix <- cor(df_corr[,c("index","Performance","Social","Attractiveness","rosenberg")])


df_corr2_menstruation = df_corr[df_corr$phase=="menstruation",c("index","Performance","Social","Attractiveness","rosenberg")]

library(Hmisc)
rcorr(as.matrix(df_corr2_menstruation),type="pearson")
```

```{r}

df_corr2_ovulation = df_corr[df_corr$phase=="ovulation",c("index","Performance","Social","Attractiveness","rosenberg")]

library(Hmisc)
rcorr(as.matrix(df_corr2_ovulation),type="pearson")
```


```{r}
#d = df_merged3
#d$predicted <- predict(model)   # Save the predicted values
#d$residuals <- residuals(model) # Save the residual values
#ggplot(d, aes(x = wt, y = mpg)) +
#  geom_smooth(method = "lm", se = FALSE, color = "lightgrey") +     # regression line  
#  geom_segment(aes(xend = wt, yend = predicted), alpha = .2) +      # draw line from point to line
#  geom_point(aes(color = abs(residuals), size = abs(residuals))) +  # size of the points
#  scale_color_continuous(low = "green", high = "red") +             # colour of the points mapped to residual #size - green smaller, red larger
#  guides(color = FALSE, size = FALSE) +                             # Size legend removed
#  geom_point(aes(y = predicted), shape = 1) +
#  theme_bw()
```

```{r}
#plot_model(model, type = "pred", terms = c("phase"))
```

```{r}
noise <- emmeans(model,~phase)


x = contrast(noise, "pairwise", simple = "each", combine = TRUE, adjust="bonf")
x
```

```{r}
eff_size(noise, sigma=sigma(model), edf = df.residual(model))
```

```{r}
#standardize
#model = lmer(rosenberg ~ contrabalanceamento*phase+fase_start+(1|participant), df_merged3)
model = lmer(rosenberg ~ phase+(1|participant), df_merged3)
tab_model(model)
```

```{r}
summary(model)
```

```{r}
#plot_model(model, type = "pred", terms = c("phase","contrabalanceamento"))
```

```{r}
#plot_model(model, type = "pred", terms = c("contrabalanceamento","phase","fase_start"))
```

```{r}
noise <- emmeans(model,~phase)


x = contrast(noise, "pairwise", simple = "each", combine = TRUE, adjust="bonf")
x
```

```{r}
eff_size(noise, sigma=sigma(model), edf = df.residual(model))
```


```{r}
#plot(df_merged3$index_global,df_merged3$rosenberg)

```

```{r}
library("lme4")
#model = lmer(index_global~phase*rosenberg + (1|participant),df_merged3)
#tab_model(model)
```

#check prime_val accuracy
```{r}
#model = glmer(correct~prime_val*phase+(1|participant),brutos)
#tab_model(model)
```

#check prime_val accuracy
```{r}
model = glmer(rt~prime_val*phase+(1|participant),brutos)
tab_model(model)
```
```{r}
brutos %>% group_by(phase, prime_val) %>% summarise(n())  


observed_table <- matrix(c(5220,5518,5362,5658), nrow = 2, ncol = 2, byrow = F)
rownames(observed_table) <- c('negative',"positive")
colnames(observed_table) <- c('menstruation', 'ovulation')
observed_table

X <- chisq.test(observed_table)
X

```

### response~val*type
```{r}
brutos$correct = factor(brutos$correct)
model = glmer(correct~prime_val*prime_type + phase*prime_val + (1|participant),family = binomial, brutos)


tab_model(model)

```
```{r}
summary(model)
```

```{r}
library(emmeans)
noise <- emmeans(model,~prime_val*prime_type)


x = contrast(noise, "pairwise", simple = "each", combine = TRUE, adjust="bonf")
x
```

```{r}
eff_size(noise, sigma=sigma(model), edf = df.residual(model))
```

